### 2020-04-08 writeup/setup.tex
change
proof
multi-task training

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.

	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
\end{enumerate}

Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediciton labels/tasks for every image \cite{EA20}.
\todo{We show the following results.}

@@

\begin{lemma}\label{lem_minv}
	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
\end{lemma}

>>>>

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer. [\textbf{done}]

	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs. [\textbf{1/2 done}]
\end{enumerate}

Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
\todo{We show the following results.} [\textbf{1/2 done}]

@@

\begin{lemma}\label{lem_minv}
	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
	%{\color{blue} \[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p} . \]}
	%\bigtr{\Sigma_2^{-1}}
\end{lemma}
